The Evolution of Phenotypically Invariant Genetic Networks

### 2017-11-10 kalman_walk_paper.tex
overleaf edits

% Other title ideas:
%
% More than one way to grow a cat: speciation despite conservation of phenotype
%
% More than one way to grow a cat: regulatory network drift and speciation
%
% Rapid speciation despite conservation of phenotype
%
% More than one way to grow a cat: regulatory network redundancy and speciation
%
% Neutral network drift leads to incompatibilities on the same time scale as genetic drift
%
% More than one way to grow a cat: can network drift lead to speciation?
%
% How fast does network drift create incompatibilities?
%
% Beyond the snowball: a quantitative model of incompatibility accumulation
%
% Systems drift and speciation: more than one way to grow a cat
%
% An explicit model of neutral regulatory network evolution, with applications
% to the rate of accumulation of hybrid incompatibility
%
% Evolutionary conservation of phenotype does not entail conservation of the underlying
% molecular mechanism leading to rapid speciation
%
% The evolution of phenotype-invariant gene networks rapidly leads to hybrid incompatibiliy
%
% Evolutionary network rewiring can rapidly lead to hybrid incompatibility despite
% phenotypic conservation
%
% Hybrid incompatibilities can evolve rapidly due to developmental systems drift
%
% Evolutionary systems theory and speciation

@@

@@

\paragraph{Hybridization}
The means of two allopatric populations each of effective size $N_e$ separated for $T$ generations
will be a distance roughly of order $2\sigma_N \sqrt{T/N_e}$ apart along $\optx$.
(Consult figure \ref{fig:conceptual_fig} for a conceptual diagram.)
A population of $F_1$ hybrids has one haploid genome from each,
whose coefficients are averaged,
and so will have mean system coefficients at the midpoint between their means.
Each $F_2$ hybrid will be homozygous for one parental allele on average at half of the loci in the genome,
so the distribution of $F_2$s will have mean at the average of the two populations,
but will have higher variance.
Concretely, we expect the population of $F_1$s to have variance $\sigma^2_S$ in the selected direction
(the same as within each parental population),
but the population of $F_2$s will have variance of order $\sigma^2_S + \sigma^2_H T/N_e$,
where $\sigma^2_H$ is a factor that depends on the genetic basis of the coefficients.
\plr{say something about $\sigma_H$?}

What are the fitness consequences?
If a population has a Gaussian distribution of trait values with variance $\sigma^2$
and fitness decays as $\exp(-x^2/2\gamma)$ away from the population mean,
then the population mean fitness is 
\begin{align*}
   \int \frac{1}{\sigma \sqrt{2\pi}} e^{-\frac{x^2}{2\sigma^2}} e^{-\frac{x^2}{2\gamma^2}} dx
   &=
   \sqrt{\frac{1}{1 + (\sigma/\gamma)^2}}  \le \frac{1}{\sigma/\gamma} .
\end{align*}
If $\sigma$ is much smaller than $\gamma$, the fitness consequences of variation
(i.e., genetic load) are small,
but if $\sigma$ is of order $\gamma$, then mean fitness is inversely proportional to trait variance
(i.e., $\gamma/\sigma$).
This implies that we expect $\sigma_S < \gamma$
but that once $T$ is of order $N_e (\gamma / \sigma_H)^2$, there will be loss of fitness
in $F_2$ hybrids.
Said another way,
if we write $\mathcal{F}(T)$ as the mean fitness of an $F_2$ hybrid between two populations separated by $T$ generations,
then fitness drops with the square root of $T$, measured in units of $N_e$ generations:
\begin{align*}
   \mathcal{F}(T) \le \frac{1}{\sigma_H/\gamma}\sqrt{\frac{N_e}{T}} .
\end{align*}

@@

\begin{align*}
\int_{-\infty}^\infty \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{(x-\mu)^2}{2\sigma^2}} e^{-\frac{x^2}{2\gamma^2}} dx
&=
\sqrt{\frac{1}{1 + \sigma^2/\gamma^2}} \exp\left\{-\frac{\mu^2}{\gamma^2}\left(\frac{1}{1 + \sigma^2/\gamma^2}\right)\right\} \\
% &\approx
% \frac{1}{\sigma/\gamma}\left(1 - \frac{\mu^2}{\gamma^2}\right) .
\end{align*}
With $\sigma = c_\sigma \gamma \sqrt{T/N_e}$
and $\mu = c_\mu \gamma (T/N_e)^2$,
this is
$$
\sqrt{\frac{1}{1 + c_\sigma^2 T/N_e}} \exp\left\{-c_\mu^2 \frac{T^2}{N_e^2} \left(\frac{1}{1 + c_\sigma^2 T/N_e}\right)\right\} \\
$$

\plri{improve figure by putting labels on from the following}
Suppose that two populations have drifted independently to differ by $z$,
and that $z$ is of the same order as $\sigma$ but is smaller than $\gamma$.
The mean $F_1$ is the average of the parental means,
and since the first-order terms in the Taylor series vanish,
has phenotype differing from the optimum by a distance of order $\|z\|^2$ 
(see appendix \ref{apx:away_from_opt}).
The mean $F_2$ is the same,
but the standard deviation is of order $z$,
so that up to lower order terms, 
while the typical fitness of an individual in the original population is
$\fit_0 = \exp(-(\sigma_s/\gamma)^2)$;
of an $F_1$ is
$\fit_1/\fit_0 = \exp(-(c_1 \sigma_N^2 T/N_e)^2)$;
and of an $F_2$ is
$\fit_2/\fit_0 = \exp(- T/(N_e\gamma^2))$.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
%
%\jss{Discussion guidelines:
%\begin{itemize}
%    \item Why is this important/useful?
%    \item What are the assumptions and shortcomings of the research?
%    \item Compare to other studies in the literature. 
%    \item Future directions. 
%    \item Wild speculations?
%    \item Conclusion and overall impact. 
%\end{itemize}}
%
The complexity of biological systems has limited our understanding of their function and evolution. Above we outline an approach, a first step, towards untangling this complexity in reference to function and evolution. This methodology borrows successfully applied tools from engineering and aims to synthesize these with the concepts and tools of molecular and evolutionary biology.

Theoretical models in evolution and population genetics often lack the molecular details of physiology or of the genotype-phenotype map. 
Here, we offer a tractable and simple model which includes these missing features. 
Further, we provide, in clear mathematical language, an analytical description of phenomena hitherto discussed verbally and conceptually 
(phenogenetic drift \citep{weiss2000phenogenetic}, developmental systems drift \citep{true2001developmental}, biological degeneracy \citep{edelman2001degeneracy}, \emph{etc.}). 
The tractability and relative simplicity of this exposition enables the interested biologist to work out by hand, 
if desired, 
the dynamics of a genetic system, as well as perturbations to the system -- an attribute not likely to be found in less tractable models and simulations.

We have suggested an interpretation of system identification: to see it as an evolutionarily neutral manifold, and not simply a computational nuisance. 
We have demonstrated a method to analytically determine the set of all phenotypically invariant gene networks; 
by a simple change of coordinates in the minimal configuration, or more generally by applying the Kalman decomposition in higher dimensions. 
%Further, we emphasize that evolution proceeds through this high dimensional space as stochastic coordinate transformation, constrained by sexual reproduction and selection. 
This set is explored over evolutionary time when phenotype is conserved, and can lead to a diverse set of consequences, 
including the accumulation of Dobzhansky-Muller incompatibilities. 
\plr{check original Bateson/DM papers to see if this accords with those defns}\js{I read through Orr's review of those papers, which included excerpts. It seems like the DMI definition is very general and this accords.}
We emphasize that these incompatibilities are a consequence of recombining different, yet functionally equivalent, mechanisms.
\plr{See refs in Barton 2010 paper.}

Furthermore, using a quantitative genetic approach, we estimated that a genetically variable population will drift in neutral system space 
at a rate determined by its intra-population variation and its effective population size. 
Because mechanistically distinct yet phenotypically equivalent biological systems can fail to produce viable hybrids, we predict allopatric populations to accumulate genetic incompatibilities 
at a rate on the order of $N_{e}$ if intrapopulation regulatory variation is constrained by selection.
Additionally we see second-generation hybrid fitness plummet much faster than that of first-generation hybrids. 
\plr{refer to Turelli here}
%This is a consequence of combining our mechanistic model with a quantitative genetic one: 
%we observe that $F_{1}$ phenotypes diverge quartically, and $F_{2}$ phenotypes quadratically, with evolutionary time. 
%\plr{awkward phrasing}
This result is also consistent with Haldane's rule; that if only one hybrid sex is inviable or sterile it is likely the heterogametic sex. 
The consistency comes from gene networks localized to the sex chromosomes functioning as an $F_{2}$ hybrid cross within a diploid $F_{1}$ heterogamete as there is only one sex chromosome.

%We also suggest that gene networks may not always use their components parsimoniously 
%as network size tends to ratchet up in the absence of strong selection against extra parts. 
%\plr{probably shouldn't claim this is "unexplored"} \js{I meant unexplored within this paper.Changed wording. Does that work?}
%Although we leave this question unexplored, this phenomena may lead to insights on evolvability and developmental innovation. 
Lastly, we show that hybrid gene networks, under neutral processes, break down as function of genetic distance, and may, in part, explain broad patterns of reproductive isolation among diverse phyla \citep{roux2016shedding}.

Note that this follows directly from the fact that $F_1$ and $F_2$ hybrid phenotypes diverge from $F_0$ phenotypes, linearly and inverse-quadratically, with respect to time (more precisely $T/N_e$). As such, removing assumptions about the form of the fitness function, this model still predicts hybrid $F_2$ phenotypes to diverge much faster than $F_1$s, initially.
So even if fitness isn't as above maybe you can see this in phenotypes.

What about nonlinearity?

Note that the drift above could actually be caused by the optimal phenotype shifting.

%\plr{this paragraph isn't very clear} \js{Should I delete it? I guess it's sort of just a vague ``yeah we know this method has shortcomings''.}
%As Richard Levins opined, models in population biology face a trade-off among precision, realism, and generality \citep{levins1966strategy}. As Levins expects, any tractable and general model, such as the present one under discussion, will have limitations. Most notable is linearity. It is often stated that life is not linear. This is often true, however, many of the ideas developed here should be generalizable to nonlinear cases (multi-linear systems, say). Further, we see this as a necessary first step in the direction of more life-like nonlinear evolutionary systems theory. Depending on an actual biological system's particularities, its (potential) non-linearity, may buffer or exacerbate effects elucidated in this paper, such as the acquisition of Dobzansky-Muller incompatibilities.

@@

%\jss{literature comparison -- I think we should delete}
%
%Over the last several years, several different computational approaches have been applied to study reproductive incompatibility and speciation. \citet{tulchinsky} simulated the evolution of a transcription factor and its binding site using a thermodynamic model. Their simulations suggest that the language by which a transcription factor recognizes its binding site can change, and potentially lead to hybrid incompatibility when allopatric populations employ divergent readout languages. This study, despite looking at gene regulation, does not analyze overall gene network architecture -- as we do here -- it only looks at the expression level of a single gene. Furthermore, they report reproductive isolation primarily following directional selection for a change in expression levels in each allopatric population; the evidence for reproductive isolation following balancing selection is much weaker. Johnson and Porter 2000 did not observe any hybrid fitness declines under stabilizing selection -- only under directional selection. 
%\plr{citations:}
%Khatari et al, Tulchinsky et al, and Porter et al, all study hybrid incompatibility from a transcription factor/binding site interaction perspective, not from an overall network architecture perspective. Palmer and Feldman only see hybrid incompatibility in constant environments if the parental populations are relatively poorly adapted initially. Otherwise hybrids between two allopatric populations have fairly high fitnesses.

@@

%%%%%%%%%%%
\subsection*{Evolution of segregation covariance}

>>>>

% Other title ideas:
%
% Rapid speciation despite conservation of phenotype
%
% How fast does network drift create incompatibilities?
%
% More than one way to grow a cat: speciation despite conservation of phenotype
%
% More than one way to grow a cat: regulatory network drift and speciation
%
% More than one way to grow a cat: regulatory network redundancy and speciation
%
% Neutral network drift leads to incompatibilities on the same time scale as genetic drift
%
% More than one way to grow a cat: can network drift lead to speciation?
%
% Beyond the snowball: a quantitative model of incompatibility accumulation
%
% Systems drift and speciation: more than one way to grow a cat
%
% An explicit model of neutral regulatory network evolution, with applications
% to the rate of accumulation of hybrid incompatibility
%
% Evolutionary conservation of phenotype does not entail conservation of the underlying
% molecular mechanism leading to rapid speciation
%
% The evolution of phenotype-invariant gene networks rapidly leads to hybrid incompatibiliy
%
% Evolutionary network rewiring can rapidly lead to hybrid incompatibility despite
% phenotypic conservation
%
% Hybrid incompatibilities can evolve rapidly due to developmental systems drift
%
% Evolutionary systems theory and speciation

@@

AND THESE?
Over the last several years, several different computational approaches have been applied to study reproductive incompatibility and speciation. \citet{tulchinsky} simulated the evolution of a transcription factor and its binding site using a thermodynamic model. Their simulations suggest that the language by which a transcription factor recognizes its binding site can change, and potentially lead to hybrid incompatibility when allopatric populations employ divergent readout languages. This study, despite looking at gene regulation, does not analyze overall gene network architecture -- as we do here -- it only looks at the expression level of a single gene. Furthermore, they report reproductive isolation primarily following directional selection for a change in expression levels in each allopatric population; the evidence for reproductive isolation following balancing selection is much weaker. Johnson and Porter 2000 did not observe any hybrid fitness declines under stabilizing selection -- only under directional selection. 
Khatari et al, Tulchinsky et al, and Porter et al, all study hybrid incompatibility from a transcription factor/binding site interaction perspective, not from an overall network architecture perspective. Palmer and Feldman only see hybrid incompatibility in constant environments if the parental populations are relatively poorly adapted initially. Otherwise hybrids between two allopatric populations have fairly high fitnesses.  
MAKE SURE TO REF DMI LIT SOMEWHERE and Barton's paper.

@@

\paragraph{Hybridization}
The means of two allopatric populations each of effective size $N_e$ separated for $T$ generations
will be a distance roughly of order $2\sigma_N \sqrt{T/N_e}$ apart along $\optx$.
(Consult figure \ref{fig:conceptual_fig} for a conceptual diagram.)
A population of $F_1$ hybrids has one haploid genome from each,
whose coefficients are averaged,
and so will have mean system coefficients at the midpoint between their means.
Each $F_2$ hybrid will be homozygous for one parental allele on average at half of the loci in the genome,
so the distribution of $F_2$s will have mean at the average of the two populations,
but will have higher variance.
The variance of $F_2$s can be shown to increase linearly with the square of the distance between
parental population means
under models of both simple and polygenic traits.
This is suggested by figure \ref{fig:conceptual_fig} and shown in Appendix \ref{apx:seg_cov}.
Concretely, we expect the population of $F_1$s to have variance $\sigma^2_S$ in the selected direction
(the same as within each parental population),
but the population of $F_2$s will have variance of order $\sigma^2_S + 4 \omega \sigma^2_N T/N_e$,
where $\omega$ is a factor that depends on the genetic basis of the coefficients.
In a model of $p$ traits in which the optimal set $\allS$ has dimension $q$,
% if each trait is controlled by a single locus, $\omega = XXX$,
using the polygenic model of appendix \ref{apx:seg_cov}, $\omega = (p-q)/8$.
If each trait is controlled by a single locus, as in figure \ref{fig:conceptual_fig},
the value is similar.

What are the fitness consequences?
A population of $F_2$s will begin to be substantially less fit than the parentals
once they differ from the optimum by a distance of order $\gamma$,
i.e., once $\sqrt{4 \omega T/N_e} \approx \gamma / \sigma_N$.
This implies that hybrid incompatibility among $F_2$s should appear on a time scale of 
$N_e \gamma / \sigma_N$ generations.
The $F_1$s will not suffer fitness consequences until the hybrid mean is further than $\gamma$ from the optimum;
as shown in appendix \ref{apx:away_from_opt} (and suggested by figure \ref{fig:conceptual_fig},
this deviation of the mean from optimum grows with the square of the distance between the parental populations,
and so we expect fitness costs in $F_1$s to appear on a time scale of $N_e^2$ generations.

If a population has a Gaussian distribution of trait values with variance $\sigma^2$
and fitness decays as $\exp(-x^2/2\gamma)$ away from the population mean,
then the population mean fitness is 
\begin{align*}
   \int \frac{1}{\sigma \sqrt{2\pi}} e^{-\frac{x^2}{2\sigma^2}} e^{-\frac{x^2}{2\gamma^2}} dx
   &=
   \sqrt{\frac{1}{1 + (\sigma/\gamma)^2}}  \le \frac{1}{\sigma/\gamma} .
\end{align*}
If $\sigma$ is much smaller than $\gamma$, the fitness consequences of variation
(i.e., genetic load) are small,
but if $\sigma$ is of order $\gamma$, then mean fitness is inversely proportional to trait variance
(i.e., $\gamma/\sigma$).
This implies that we expect $\sigma_S < \gamma$
but that once $T$ is of order $N_e (\gamma / \sigma_H)^2$, there will be loss of fitness
in $F_2$ hybrids.
Said another way,
if we write $\mathcal{F}(T)$ as the mean fitness of an $F_2$ hybrid between two populations separated by $T$ generations,
then fitness drops with the square root of $T$, measured in units of $N_e$ generations:
\begin{align*}
   \mathcal{F}(T) \le \frac{1}{\sigma_H/\gamma}\sqrt{\frac{N_e}{T}} .
\end{align*}

@@

\begin{align*}
\int_{-\infty}^\infty \frac{1}{\sigma\sqrt{2\pi}} e^{-\frac{(x-\mu)^2}{2\sigma^2}} e^{-\frac{x^2}{2\gamma^2}} dx
&=
\sqrt{\frac{1}{1 + \sigma^2/\gamma^2}} \exp\left\{-\frac{\mu^2}{\gamma^2}\left(\frac{1}{1 + \sigma^2/\gamma^2}\right)\right\} \\
% &\approx
% \frac{1}{\sigma/\gamma}\left(1 - \frac{\mu^2}{\gamma^2}\right) .
\end{align*}
With $\sigma/\gamma = c_\sigma \sqrt{T/N_e}$
and $\mu/\gamma = c_\mu T/N_e$,
this is (check!!)
$$
\sqrt{\frac{1}{1 + c_\sigma^2 T/N_e}} \exp\left\{-c_\mu^2 \frac{T^2}{N_e^2} \left(\frac{1}{1 + c_\sigma^2 T/N_e}\right)\right\} \\
$$

@@

If $\sigma_N \approx \sigma_S \approx \gamma$ and variance in $F_2$s increases linearly with distance betw parents,
then fitness starts to drop at $T/4N_e$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}

%%% OUTLINE
% - Summarize methods and main result on rate of speciation.
% - What empirical evidence is there that this is actually happening? 
%   * incompats due to misregulation (Noor, Witkopp...)
%   * numerous species that are visually indistinguishable (skinks, ferns)
%   * maybe also ref phylogenetic lit
% - What other evidence could be collected?  Note could be just phenotype not fitness. (cite Matute)
% - Is linearity an important assumption?
% - We know that divergent selection and genetic conflict can easily lead to speciation; we've shown neutral drift can maybe surprisingly easily do so also; but it remains unclear the relative contributions of these. Note that although drift may be weaker in any one network there are lots of networks. Could motivate this with Orr's statement.  Perhaps tie in spandrels.

% we do cool stuff
The complexity of biological systems has limited our understanding of their function and evolution. Above we outline an approach, a first step, towards untangling this complexity in reference to function and evolution. This methodology borrows successfully applied tools from engineering and aims to synthesize these with the concepts and tools of molecular and evolutionary biology.

% no, really, it's cool
Theoretical models in evolution and population genetics often lack the molecular details of physiology or of the genotype-phenotype map. 
Here, we offer a tractable and simple model which includes these missing features. 
Further, we provide, in clear mathematical language, an analytical description of phenomena hitherto discussed verbally and conceptually 
(phenogenetic drift \citep{weiss2000phenogenetic}, developmental systems drift \citep{true2001developmental}, biological degeneracy \citep{edelman2001degeneracy}, \emph{etc.}). 
The tractability and relative simplicity of this exposition enables the interested biologist to work out by hand, 
if desired, 
the dynamics of a genetic system, as well as perturbations to the system -- an attribute not likely to be found in less tractable models and simulations.

% it says something about speciation and DMIs
We have suggested an interpretation of system identification: to see it as an evolutionarily neutral manifold, and not simply a computational nuisance. 
We have demonstrated a method to analytically determine the set of all phenotypically invariant gene networks; 
by a simple change of coordinates in the minimal configuration, or more generally by applying the Kalman decomposition in higher dimensions. 
%Further, we emphasize that evolution proceeds through this high dimensional space as stochastic coordinate transformation, constrained by sexual reproduction and selection. 
This set is explored over evolutionary time when phenotype is conserved, and can lead to a diverse set of consequences, 
including the accumulation of Dobzhansky-Muller incompatibilities. 
\plr{check original Bateson/DM papers to see if this accords with those defns}\js{I read through Orr's review of those papers, which included excerpts. It seems like the DMI definition is very general and this accords.}
We emphasize that these incompatibilities are a consequence of recombining different, yet functionally equivalent, mechanisms.
\plr{See refs in Barton 2010 paper.}

% summary and consequences of main result on speed of speciation
Furthermore, using a quantitative genetic approach, we estimated that a genetically variable population will drift in neutral system space 
at a rate determined by its intra-population variation and its effective population size. 
Because mechanistically distinct yet phenotypically equivalent biological systems can fail to produce viable hybrids, we predict allopatric populations to accumulate genetic incompatibilities 
at a rate on the order of $N_{e}$ if intrapopulation regulatory variation is constrained by selection.
Additionally we see second-generation hybrid fitness plummet much faster than that of first-generation hybrids. 
\plr{refer to Turelli here}
%This is a consequence of combining our mechanistic model with a quantitative genetic one: 
%we observe that $F_{1}$ phenotypes diverge quartically, and $F_{2}$ phenotypes quadratically, with evolutionary time. 
%\plr{awkward phrasing}
This result is also consistent with Haldane's rule; that if only one hybrid sex is inviable or sterile it is likely the heterogametic sex. 
The consistency comes from gene networks localized to the sex chromosomes functioning as an $F_{2}$ hybrid cross within a diploid $F_{1}$ heterogamete as there is only one sex chromosome.
%We also suggest that gene networks may not always use their components parsimoniously 
%as network size tends to ratchet up in the absence of strong selection against extra parts. 
%\plr{probably shouldn't claim this is "unexplored"} \js{I meant unexplored within this paper.Changed wording. Does that work?}
%Although we leave this question unexplored, this phenomena may lead to insights on evolvability and developmental innovation. 
Lastly, we show that hybrid gene networks, under neutral processes, break down as function of genetic distance, and may, in part, explain broad patterns of reproductive isolation among diverse phyla \citep{roux2016shedding}.

Do we see evidence of this?  Well, maybe: misregulation in hybrids in Witkopp, Noor, Barbash, etc,
even with expression levels in parents being the same.

% consequence: prediction for phenotype (not just fitness)
Note that this follows directly from the fact that $F_1$ and $F_2$ hybrid phenotypes diverge from $F_0$ phenotypes, linearly and inverse-quadratically, with respect to time (more precisely $T/N_e$). As such, removing assumptions about the form of the fitness function, this model still predicts hybrid $F_2$ phenotypes to diverge much faster than $F_1$s, initially.
So even if fitness isn't as above maybe you can see this in phenotypes.

% nonlinearity
What about nonlinearity?
As Richard Levins opined, models in population biology face a trade-off among precision, realism, and generality \citep{levins1966strategy}. As Levins expects, any tractable and general model, such as the present one under discussion, will have limitations. Most notable is linearity. It is often stated that life is not linear. This is often true, however, many of the ideas developed here should be generalizable to nonlinear cases (multi-linear systems, say). Further, we see this as a necessary first step in the direction of more life-like nonlinear evolutionary systems theory. Depending on an actual biological system's particularities, its (potential) non-linearity, may buffer or exacerbate effects elucidated in this paper, such as the acquisition of Dobzansky-Muller incompatibilities.

% selection moving around optimal set
Note that the drift above could actually be caused by the optimal phenotype shifting.

@@

% J and P didn't get speciation in a neutral  model
Discuss differences to Johnson and Porter.

What is Ne?  In a metapopulation depends on migr rate: classic Turelli paper.

@@

%%%%%%%%%%%
\subsection*{Evolution of segregation covariance}
\label{apx:seg_cov}
